Abstract Data Type Inference

### 2015-03-10 algebra.tex
Note on width-bounded kernels.

The previous example demonstrates that $\preceq$ is not a wqo by allowing each
history $h_i$ of the infinite sequence to contain more and more pending
operations in order to ensure that $h_j \not\preceq h_i$ for every $j < i$.
Curbing this ability by limiting the maximum amount of pending operations per
history makes $\preceq$ a wqo. Although limiting to $k$ pending operations
essentially limits us to histories of executions with at most $k$ operations
parallel at any moment — e.g.,~of programs with at most $k$ threads — this
restriction comes at no loss of completeness when considering atomic ATD
kernels, whose histories are limited to $k\!=\!1$ pending operation.

@@

@@

  $\preceq$ is a wqo on the set of histories with at most $k$ pending
  operations, for any $k \in \mathbb{N}$.

>>>>

The previous example demonstrates that $\preceq$ is not a wqo by allowing each
history $h_i$ of the infinite sequence to contain more and more pending
operations in order to ensure that $h_j \not\preceq h_i$ for every $j < i$.
Curbing this ability by limiting the maximum amount of pending operations per
history makes $\preceq$ a wqo. Although limiting to $k$ pending operations
essentially limits us to width-$k$ histories, of executions with at most $k$
operations parallel at any moment — e.g.,~of programs with at most $k$ threads
— this restriction comes at no loss of completeness when considering atomic ADT
kernels, which have width $1$.

@@

TODO DEFINE A TERM FOR ADTS WHOSE KERNELS HAVE BOUNDED WIDTH

@@

  $\preceq$ is a wqo on width-$k$ histories, for any $k \in \mathbb{N}$.
